% This template was initially provided by Dulip Withanage.
% Modifications for the database systems research group
% were made by Conny Junghans,  Jannik Strötgen and Michael Gertz

\documentclass[
     12pt,         % font size
     a4paper,      % paper format
     BCOR10mm,     % binding correction
     DIV14,        % stripe size for margin calculation
     ]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% PACKAGES:

% Use German :
\usepackage[english]{babel}
% Input and font encoding
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
% Index-generation
\usepackage{makeidx}
% Einbinden von URLs:
\usepackage{url}
% Special \LaTex symbols (e.g. \BibTeX):
%\usepackage{doc}
% Include Graphic-files:
\usepackage{graphicx}
% Include doc++ generated tex-files:
%\usepackage{docxx}
% Fuer anderthalbzeiligen Textsatz
\usepackage{setspace}
% hyperrefs in the documents
\PassOptionsToPackage{hyphens}{url}\usepackage[bookmarks=true,colorlinks,pdfpagelabels,pdfstartview = FitH,bookmarksopen = true,bookmarksnumbered = true,linkcolor = black,plainpages = false,hypertexnames = false,citecolor = black,urlcolor=black]{hyperref}
%\usepackage{hyperref}


% CUSTOM:

\usepackage{csquotes}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% OTHER SETTINGS:

% Choose language
\newcommand{\setlang}[1]{\selectlanguage{#1}\nonfrenchspacing}


\begin{document}

% TITLE:
\pagenumbering{roman} 
\begin{titlepage}

\vspace*{1cm}
\begin{center}
\textbf{ 
\Large Heidelberg University\\
\smallskip
\Large Institute of Computer Science\\
\smallskip
\Large Database Systems Research Group\\
\smallskip
}

\vspace{3cm}

\textbf{\large Report for the lecture Text Analytics}

\vspace{0.5\baselineskip}
{\huge
\textbf{Hate Speech Detection}
}
\vspace{0.5cm}

\url{https://github.com/fidsusj/HateSpeechDetection}

\vspace{1cm}
Mentor: John Ziegler
\end{center}

\vfill 

{\large
\begin{tabular}[l]{ll}
Team Member: & Christopher Klammt, 3588474,\\
  & Applied Computer Science\\
  & iv249@stud.uni-heidelberg.de\\
  & \\
Team Member: & Felix Hausberger, 3661293,\\
  & Applied Computer Science\\
  & eb260@stud.uni-heidelberg.de\\
  & \\
Team Member: & Nils Krehl, 3664130,\\
  & Applied Computer Science\\
  & pu268@stud.uni-heidelberg.de\\
  
\end{tabular}
}

\end{titlepage}

\pagenumbering{arabic}

\input{content/abstract.tex}
\input{content/anti-plagiarism-statement.tex}

\newpage
\tableofcontents
\newpage

\input{content/introduction.tex}
\input{content/related-work.tex}
\input{content/approach.tex}
\input{content/experimental-setup.tex}
\input{content/analysis.tex}
\input{content/conclusion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\bibliographystyle{plain}
% \bibliography{references}
\begin{thebibliography}{9}
	
\bibitem{Dorris2020} Dorris, W., Hu, R., Vishwamitra, R., Luo, F., Costello, M.: Towards Automatic Detection and Explanation of Hate Speech and Offensive Language.
In: Proceedings of the Sixth International Workshop on Security and Privacy Analytics (2020).
https://doi.org/10.1145/3375708.3380312

\bibitem{Syam2019} Syam, S., Irawan, B., Setianingsih, C.: Hate Speech Detection on Twitter Using Long Short-Term Memory (LSTM) Method.
In: 4th International Conference on Information Technology, Information Systems and Electrical Engineering (ICITISEE) (2019).
https://doi.org/10.1109/ICITISEE48480.2019.9003992

\bibitem{Saksesi2018} Saksesi, A., Nasrun, M., Setianingsih, C.: Analysis Text of Hate Speech Detection Using Recurrent Neural
Network.
In: International Conference on Control, Electronics, Renewable Energy and Communications (ICCEREC) (2018).
https://doi.org/10.1109/ICCEREC.2018.8712104

\bibitem{Founta2019} Founta, A., Chatzakou, D., Kourtellis, N., Blackburn, J., Vakali, A., Leontiadis, I.: A Unified Deep Learning Architecture for Abuse Detection.
In: Proceedings of the 10th ACM Conference on Web Science (2019).
https://doi.org/10.1145/3292522.3326028

\bibitem{Saleh2020} Saleh, H., Alhothali, A., Moria, K.: Detecting White Supremacist Hate Speech using Domain Specific Word Embedding with Deep Learning and BERT.
In: arXiv (2020).
https://arxiv.org/abs/2010.00357

\bibitem{Badjatiya2017} Badjatiya, P., Gupta, S., Gupta, M., Varma, V.: Deep Learning for Hate Speech Detection in Tweets.
In: Proceedings of the 26th International Conference on World Wide Web Companion (2017).
https://doi.org/10.1145/3041021.3054223

\bibitem{Roy2020} Roy, P., Tripathy, A., Das, T., Gao, X.: A Framework for Hate Speech Detection Using Deep Convolutional Neural Network.
In: IEEE Access (Volume: 8) (2020).
https://doi.org/10.1109/ACCESS.2020.3037073

\bibitem{Kapil2020} Kapil, P., Ekbal, A., Das, D.: Investigating Deep Learning Approaches for Hate Speech Detection in Social Media.
In: arXiv (2020).
https://arxiv.org/abs/2005.14690

\bibitem{Muhammad2020} Muhammad, I., Nasrun, M., Setianingsih, C.: Hate Speech Detection using Global Vector and Deep Belief Network Algorithm.
In: 1st International Conference on Big Data Analytics and Practices (IBDAP) (2020).
https://doi.org/10.1109/IBDAP50342.2020.9245467

\end{thebibliography}

\end{document}